### 2025-11-28 paper/sections/other/main_results.qmd
updated to v1.12

using CTExperiments
using CTExperiments.CairoMakie
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.Plots
using CTExperiments.PrettyTables
using CTExperiments.StatsBase
using Random
using Serialization

>>>>

using CTExperiments
using CTExperiments.Makie
using CTExperiments.CSV
using CTExperiments.DataFrames
using CTExperiments.Plots
using CTExperiments.PrettyTables
using CTExperiments.StatsBase
using Random
using Serialization
